forrechelle

### 2019-12-20 analysis/20_forrechelle.Rmd
working on candidate gnee plots

knitr::opts_chunk$set(echo = TRUE)
```

@@

candidategenes <- c( "GH", "NR3C2", "PRLR", "PRL")
timepoints <- c("lay" , "inc.d9", "hatch", "n9")
hormones <- c("PRL", "CORT")

@@

```{r readfile}

geneids <- read_csv("..//metadata/00_geneinfo.csv")

datapath <- "../results/"   # path to the data
datafiles <- dir(datapath, pattern = "04_vsd*") # get file names
datapathfile <- paste0(datapath, datafiles)

df <- datapathfile %>%
  setNames(nm = .) %>%
  map_df(~read_csv(.x, col_types = cols(), col_names = T), .id = "filename") %>% 
  mutate(tissue = sapply(strsplit(as.character(filename),'../results/04_vsd_'), "[", 2)) %>% 
  mutate(tissue = sapply(strsplit(as.character(tissue),'.csv'), "[", 1))  %>% 
  left_join(geneids) %>%
  select(tissue, X1, Name, everything()) %>% select(-filename, -geneid, - entrezid, - row.names) 
head(df)

df2 <-  df  %>%
  filter(Name %in% candidategenes) %>%
  pivot_longer(cols = L.Blu13_male_gonad_control.NYNO:y98.o50.x_male_pituitary_inc.d3, 
               names_to = "sample", values_to = "vsd") %>%
   mutate(sex = sapply(strsplit(as.character(sample),'_'), "[", 2)) %>%
   mutate(treatment = sapply(strsplit(as.character(sample),'_'), "[", 4))  %>%
   mutate(treatment = sapply(strsplit(as.character(treatment),'.NYNO'), "[", 1)) %>%
  mutate(bird = sapply(strsplit(as.character(sample),'_'), "[", 1)) %>%
  filter(treatment %in% timepoints) %>%
  select(bird, sex, treatment, tissue, Name, vsd) %>%
  rename(gene = Name)
head(df2)

@@

}
```

>>>>

source("../R/themes.R")

knitr::opts_chunk$set(echo = TRUE, fig.path = "../figures/favegenes/")
```

@@

candidategenes <- c( "NR3C1", "NR3C2", "PRLR", "PRL")
timepoints <- c("lay" , "inc.d9", "hatch", "n9")
hormones <- c("PRL", "CORT")

@@

```{r rechelle}

datapath <- "../results/"   # path to the data
datafiles <- dir(datapath, pattern = "*allvsd.csv") # get file names
datapathfile <- paste0(datapath, datafiles)

df <- datapathfile %>%
  setNames(nm = .) %>%
  map_df(~read_csv(.x, col_types = cols(), col_names = T), .id = "filename") %>% 
  mutate(tissue = sapply(strsplit(as.character(filename),'../results/06_'), "[", 2)) %>% 
  mutate(tissue = sapply(strsplit(as.character(tissue),'allvsd.csv'), "[", 1))  %>% 
  select(tissue, X1, everything()) 
head(df)

df <- df %>% filter(tissue != "gon")
head(df)

df2 <-  df  %>%
  filter(X1 %in% candidategenes) %>%
  pivot_longer(cols = L.Blu13_male_gonad_control.NYNO:y98.o50.x_male_pituitary_inc.d3, 
               names_to = "sample", values_to = "vsd") %>%
   mutate(sex = sapply(strsplit(as.character(sample),'_'), "[", 2)) %>%
   mutate(treatment = sapply(strsplit(as.character(sample),'_'), "[", 4))  %>%
   mutate(treatment = sapply(strsplit(as.character(treatment),'.NYNO'), "[", 1)) %>%
  mutate(bird = sapply(strsplit(as.character(sample),'_'), "[", 1)) %>%
  filter(treatment %in% timepoints) %>%
  select(bird, sex, treatment, tissue, X1, vsd) %>%
  rename(gene = X1) %>%
  drop_na()
head(df2)

@@

}

  p <-  df3 %>%
    filter(tissue == i) %>%
    ggplot(aes(x = treatment, y = m)) +
    geom_errorbar(aes(ymin=m-se, ymax=m+se, color=gene), width=.1) +
    geom_point(size = 1, aes(color = gene)) +
    geom_line(aes(x = as.numeric(treatment), y = m, color = gene)) +
    scale_alpha_manual(values = c(0.5, 1)) +
    labs(subtitle = i, y = "average expression", x = "parental stage") +
    facet_wrap(~sex, nrow = 1) +
    theme_B3()
  plot(p)

}
